%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	%---------------------------------------------------------
	\cventry
	{Researcher} % Job title
	{Functional Genomics Lab(Prof. Tae Hoon Kim)} % Organization
	{Richardson, Texas} % Location
	{Jul 2015 - PRESENT} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Created a pipeline to reproduce and create new eRNA
					predictions using Snakemake.}
			\item {Used techniques such as containers, conda environments, and
					high-performance computing clusters.}
			\item {Created various resources for the lab such as JupyterHub
					and the organization of the lab's documentation.}
			\item {Designed PCR primers for cell identification, target transcripts, and genotyping.}
			\item {Performed RNA isolation from cells that were treated with LPS-particles and used qPCR to quantify eRNA transcript levels.}
		\end{cvitems}
	}

	\cventry
	{Blockchain Software Engineer}
	{\href{https://www.olypsis.com/}{Olypsis Technologies}}
	{Dallas, Texas} % Location
	{May 2018 - PRESENT} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Lead developement and design of \href{https://blocknkey.com/}
			            completing tasks including, creating a functioning test
			            suite for legacy code, containerizing the entire system,
			            designing and implementing a REST API and Smart contracts
			            for the system.
			      }
			\item {Created a novel ERC20 payment splitter Smart contract in Solidity for Digital Assets
			            Foundry.}
			\item {Improved velocity by creating in house standards for CI/CD
			            for Javascript and Solidity projects using linters and test
			            suites to ensure agile developement practices through
			            automated deployments, and creating
                        auto generating documentation from inline code documentation.}
			\item {Developed the DAWN protocol to transfer files in a peer to
			            peer fashion, that is decentralized and does not rely on a
			            3rd party to be trusted using Whisper, IPFS, AES256, and React.}
			\item {Developed Smart contracts for the Saro Project to created
			            smart contracts for users to create non-fungible tokens of their real estate and
			            split the ownership of the property using fungible tokens.}
		\end{cvitems}
	}


	%---------------------------------------------------------
	% \cventry
	% {Co-founder} % Job title
	% {Millblock LLC} % Organization
	% {Richardson, Texas} % Location
	% {Sep 2017 - PRESENT} % Date(s)
	% {
	% 	\begin{cvitems} % Description(s) of tasks/responsibilities
	% 		\item {Analyzed blockchain projects and their respective cryptocurrencies as investments.}
	% 		\item {Hired and managed contractors to carry out various technical projects.}
	% 	\end{cvitems}
	% }

	%---------------------------------------------------------
	% \cventry
	%   {Apprentice} % Job title
	%   {Paul G. Hull, MD} % Organization
	%   {Plano, Texas} % Location
	%   {May 2014 - Aug 2016} % Date(s)
	%   {
	%     \begin{cvitems} % Description(s) of tasks/responsibilities
	%       \item {Learned general diagnostic techniques}
	%       \item {Sutured patients wounds after procedures.}
	%       \item {Administered various injectioins to the patients.}
	%       \item {Drew blood for routine blood tests.}
	%       \item {Learned to interpret EKGs}
	%     \end{cvitems}
	%   }

	%---------------------------------------------------------
\end{cventries}
