%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	\cventry
	{Student Researcher} % Job title
	{Functional Genomics Lab(Prof. Tae Hoon Kim)} % Organization
	{Richardson, Texas} % Location
	{Jul 2015 - PRESENT} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Created a pipeline to reproduce and create new eRNA
					predictions using Snakemake.}
			\item {Used techniques such as containers, conda environments, and
					high-performance computing clusters.}
			\item {Created various resources for the lab such as JupyterHub
					and the organization of the lab's documentation.}
			\item {Designed PCR primers for cell identification, target transcripts, and genotyping.}
			\item {Genotyped and organized the lab's various knock-out mice colonies.}
			\item {Dissected mice to retrieve the frontal cortex and then cultured the neuronal cells.}
			\item {Performed RNA isolation from cells that were treated with LPS-particles and used qPCR to quantify eRNA transcript levels.}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Software Developer} % Job title
	{Olypsis Technologies Inc.} % Organization
	{Dallas, Texas} % Location
	{May 2018 - PRESENT} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Created smart contracts for Digital Asset foundry, to allow
					users to have partial ownership in a real-estate trust.}
			\item {Designed and implemented BlockNKey, an enterprise key management solution
					that logs events with cryptographic keys on the Ethereum blockchain.}
			\item {Developed the DAWN protocol to transfer files in a peer to peer fashion, that is decentralized and does not rely on a 3rd party to be trusted.}
			\item {Built and deployed DAWN protocol using Whisper, IPFS, AES256, and React.}
			\item {Lead for Saro Project to created smart contracts for users to create non-fungible tokens of their real estate and split the ownership of the property using fungible tokens.}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Co-founder} % Job title
	{Millblock LLC} % Organization
	{Richardson, Texas} % Location
	{Sep 2017 - PRESENT} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Analyzed blockchain projects and their respective cryptocurrencies as investments.}
			\item {Hired and managed contractors to carry out various technical projects.}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Apprentice} % Job title
	{Paul G. Hull, MD} % Organization
	{Plano, Texas} % Location
	{May 2014 - Aug 2016} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Learned general diagnostic techniques}
			\item {Sutured patients' wounds after procedures.}
			\item {Administered various injections to the patients.}
			\item {Drew blood for routine blood tests.}
			\item {Learned to interpret EKGs}
		\end{cvitems}
	}

	%---------------------------------------------------------
\end{cventries}
